Viscous Transport in Eroding Porous Media

### 2019-06-10 docs/transport/erosion_transport.tex
do the result section in transport paper

Fig.~\ref{fig:Eroding20flowrate} we record the flow rate $U$ quantifily
during the eroding. Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area occupied by bodies is getting smaller $U$ is getting larger.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
with growth rate close to $\ln10^4$.

@@

In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of $\tau$ at two neighboring tracers 
and draw 
In Fig.~\ref{fig:Eroding20tort}(d) 
}

>>>>

We record the flow rate $U$ quantifily in log scale
during the eroding in Fig.~\ref{fig:Eroding20flowrate}. 
Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area occupied by bodies is getting smaller $U$ is getting larger.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
with growth rate close to $\ln10^4$.

@@

In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of $\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in Fig.~\ref{fig:Eroding20tort_traj}
if the difference of length of the neighboring trajectories is large. From this figure, we are able to 
tell the neighboring trajectories will be very different if they are separated by bodies. 
}
